Sexual selection, environmental variation, range size and speciation in passerine birds

### 2018-09-24 Manuscript.Rmd
change intro

---
title: "Sexual selection, environmental variation, range size and speciation in passerine birds"
author: 
- Justin G. Cally*\textsuperscript{§}, Iliana Medina Guzmán\textsuperscript{§}, Luke Holman\textsuperscript{§} and Devi Stuart-Fox\textsuperscript{§}
- 
- '*\textit{justin.g.cally@gmail.com}'
output:
  pdf_document: default
  html_document: default
  word_document:
      pandoc_args: ["--smart"]
bibliography: References/SS_Extinction.bib
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual Selection and Extinction} \usepackage[noabbrev,capitalise]{cleveref} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\doublespacing \usepackage[font={small}]{caption}
csl: References/AmNat.csl
abstract: Sexual selection may influence patterns of diversification. Yet their relationship remains unclear with controversy on whether sexual selection leads to a net increase or decrease in speciation rate. Sexual selection is predicted to increase speciation rate as it can facilitate adaptation to new environments by elevating the average fitness of a population. Additionally, sexual selection may work alongide divergent natural selection and swiflty promote reproductive isolation. Here we use sexual dichromatism as a proxy for sexual selection across 5,812 species of passerine birds and a multivariate male-bias measure of sexual selection (sexual dimorphism, polygyny and paternal care) across 2,465 species to investigate the association of sexual selection with speciation and extinction. Importantly, we test whether the effects of sexual selection on speciation are dependent upon ecological pressures such as temperature variability across time and space, primary productivity and range size. Our results from three distinct measures of speciation ($\lambda_{DR}$, $\lambda_{ND}$, $\lambda_{BAMM}$) and one measure of extinction ($\mu_{BAMM}$) find that male-bias sexual selection but not sexual dichromatism predicts speciation. Additionally, we find that birds with smaller ranges have higher speciation rates; however the causality of this finding remains inconclusive.
---
\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}

\newpage
#Introduction

>>>>

---
title: "Sexual selection, environmental variation, range size and speciation in passerine birds"
author: 
- Justin G. Cally*\textsuperscript{§}, Iliana Medina Guzmán\textsuperscript{§}, Luke Holman\textsuperscript{§} and Devi Stuart-Fox\textsuperscript{§}
- 
- '*\textit{justin.g.cally@gmail.com}'
output:
  word_document:
      pandoc_args: ["--smart"]
  html_document: default
  pdf_document: default
bibliography: References/SS_Extinction.bib
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual Selection and Extinction} \usepackage[noabbrev,capitalise]{cleveref} \usepackage{titlefoot}
  \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno} \linenumbers \usepackage{setspace}\doublespacing \usepackage[font={small}]{caption}
csl: References/AmNat.csl
abstract: Sexual selection may influence patterns of diversification. Yet their relationship remains unclear with controversy on whether sexual selection leads to a net increase or decrease in speciation rate. Sexual selection is predicted to increase speciation rate as it can facilitate adaptation to new environments by elevating the average fitness of a population. Additionally, sexual selection may work alongide divergent natural selection and swiflty promote reproductive isolation. Here we use sexual dichromatism as a proxy for sexual selection across 5,812 species of passerine birds and a multivariate male-bias measure of sexual selection (sexual dimorphism, polygyny and paternal care) across 2,465 species to investigate the association of sexual selection with speciation and extinction. Importantly, we test whether the effects of sexual selection on speciation are dependent upon ecological pressures such as temperature variability across time and space, primary productivity and range size. Our results from three distinct measures of speciation ($\lambda_{DR}$, $\lambda_{ND}$, $\lambda_{BAMM}$) and one measure of extinction ($\mu_{BAMM}$) find that male-bias sexual selection but not sexual dichromatism predicts speciation. Additionally, we find that birds with smaller ranges have higher speciation rates; however the causality of this finding remains inconclusive.
---
\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}

\newpage
#Introduction xxxxxx
